Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-15 paper/main.tex
methods: honing & typos (v4)

\begin{itemize}
    \item main text: add references to supplemental material
    \item imo AD and AV can be written as movie and audio-description
    \item [text in brackets] can probably be deleted
\end{itemize}

@@

\begin{itemize}
    \item check if captions of figs and tables now (really) match phrasing
        in intro / method
\end{itemize}

@@

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of the regressors used in the analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table \ref{tab:av-events})
        rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square loudness and between their left-right difference in
        loudness yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
        \todo[inline]{checked it, all labels listed}
      }
\label{fig:reg-corr}
\end{figure*}

@@

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlate with increased hemodynamic activity in the PPA.
% group level
On a group average level, we compare results gained from whole-brain GLM
analyses of the movie and the audio-description to results gained from a
traditional visual localizer \citep{sengupta2016extension}.
% individual level
On the level single subjects, we also assess the performance of the exclusively
auditory naturalistic stimulus as a substitute for a visual paradigm to localize
the PPA.
% NeuroVault
Unthresholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.

@@

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.\todo{Havard-Oxford atlas: 3 different most prob. locations depen. on
voxel}
% precuneus
Two additional clusters are apparent in the ventral precuneus extending into the
retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.

% figure group results primary AD & AV contrasts
\begin{figure*}[h!] \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (gray).
        Light gray: The audio-description's field-of-view
        (cf. \citep{hanke2014audiomovie}).
        Black: outline of overlapping individual PPA ROIs
        \citep{sengupta2016extension}.
        The results of audio-description's primary $t$-contrast (blue) that
        compares geometry-related nouns spoken by the narrator to non-spatial
        nouns (\texttt{geo, groom} > all non-spatial
        categories)
        are overlaid over the movie's primary $t$-contrast (blue) that compares
        cuts to a new setting with cuts to a familiar perspective
        (\texttt{vse\_new > vpe\_old}).
        }
    \label{fig:group-slices}
\end{figure*}

\begin{table*}[h!]
\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
    setting that was not depicted before to a recurring setting
    (\texttt{vse\_new > vpe\_old}).
    Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r.
cuneal c., intracalcarine c., bilaterally occipital fusiform g., precuneus,temporal fusiform c., posterior parahippocampal c.  \\
154 & 0.000000656 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 0.00000769 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual subjects to ensure that the group results are not just a by-product
of the averaging process.
% AD is the real shit
Further, we hypothesized that an exclusively auditory stimulus could localize
the PPA in individual subjects and thus possibly substitute a classic visual
localizer experiment.

% Sengupta et al., 2016; unilateral in sub-04 and sub-20
The visual localizer \citep{sengupta2016extension} yielded bilateral
parahippocampal clusters in 12 of 14 subjects and an unilateral right clusters
in two subjects (cf. Table 3 in \citep{sengupta2016extension}).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting unthresholded $t$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts, and titrating [?] the $t$-threshold in the range
of [2, 3] in until we found an isolated cluster (cf. Table 3 in  that matched the expected
anatomical location based on literature \citep{epstein1998ppa}.
\todo{they used $t$-maps???}
% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects (Z>2.3, p<.05
cluster-corrected for the analysis in subject-space; Z>3.4, p<.05 for the
analysis in group-space).
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset.
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space.
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
\citep{sengupta2016extension} co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

@@

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
        cluster-corrected).
        Individual brains are aligned via non-linear
        transformation to a study-specific T2* group template that is
        co-registered to the MNI152 template with an affine transformation (12
        degrees of freedom).
        The results of audio-description's primary
        $t$-contrast (blue) that compares geometry-related nouns to non
        geometry-related nouns spoken by the audio-description's narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (blue) that compares cuts to new setting with cuts
        to a familiar perspective (\texttt{vse\_new > vpe\_old}).
        Black:
        outline of subject-specific PPA ROIs.
        Light gray: The
        audio-description's field-of-view (cf. \citep{hanke2014audiomovie}).
        To facilitate comparisons across subjects, we chose the same horizontal
        slice (x=-11) for all subjects as this slice depicts voxels of
        significant clusters in almost all subjects.
        The figure does not show voxels of the left cluster of the AV stimulus
        in sub-09 and sub-18, and voxels of right cluster of the AV stimulus in
        sub-15.}
    \label{fig:subs-thresh-ppa}
\end{figure*}

% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
subject (see Figure \ref{fig:bland-altman}).
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus AD) of
two spatially corresponding voxels in the unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (see KDE plot for the x-axes
in Figure \ref{fig:bland-altman}).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show higher $z$-value in the AD stimulus.

\begin{figure*}[h!]
\centering
    \includegraphics[scale=0.27]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual subjects.
    The x-axes show the means of two spatially corresponding voxels in the
    unthresholded $z$-map of the audio-description's primary contrast and
    unthresholded $z$-map of the visual localizer (KDE plot on the top).
    The y-axes show the difference of two voxels (localizer minus
    audio-description; KDE plot on the right).
    The overlays depict voxels spatially constrained to the
    temporal and occipital cortex (gray; based on the probabilistic Jülich
    Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment}),
    PPA overlap of all subjects (blue),
    and individual PPA(s) (red).}
    \label{fig:bland-altman}
\end{figure*}

>>>>

\begin{itemize}
    \item [text in brackets] can probably be deleted
    \item imo AD and AV can be written as movie and audio-description
\end{itemize}

@@

\begin{itemize}
    \item tables: round p-values to ?
\end{itemize}

@@

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/regressor-corr} \caption{Pearson
        correlation coefficients of modeled time series used as regressors in
        the GLM analysis of the
        audio-description (blue; see Table \ref{tab:ao-events} for a
        description) and audio-visual movie (red; see Table
        \ref{tab:av-events}).
        Values are rounded to the nearest tenth.
        The correlation between the two stimuli's
        root mean square volume and between their left-right difference in
        volume yielded the highest correlation values
        (\texttt{fg\_ad\_rms} and \texttt{fg\_av\_ger\_rms}, r=.7635;
        \texttt{fg\_ad\_lrdiff} and \texttt{fg\_av\_ger\_lrdiff}, r=.7749).
        \todo[inline]{checked it, all labels listed}
      }
\label{fig:reg-corr}
\end{figure*}

@@

% study goal
We investigated if spatial information embedded in two naturalistic stimuli
correlates with increased hemodynamic activity in the PPA.
% group level
On a group average level, we compare results gained from whole-brain GLM
analyses of the movie and the audio-description to results gained from a
traditional visual localizer \citep{sengupta2016extension}.
% individual level
On the level single subjects, we also assess the performance of the exclusively
auditory naturalistic stimulus as a substitute for a visual paradigm to localize
the PPA.
% NeuroVault
Unthresholded $z$-maps of all contrasts on a group level as well as individual
results of the primary $t$-contrasts co-registered to the group-template (MNI152
space) can found at
\href{https://neurovault.org/collections/KADGMGVZ/}{NeuroVault}.
% reference to supplemental material
Results and discussion of the additional contrasts (PPA and negative controls)
can be found in the supplemental material

@@

% AD intro
Second, we analyzed data from the audio-description offering exclusively
auditory stimulation.
% AD primary contrast
The primary $t$-contrast for the audio-description (\texttt{geo, groom} >
non-spatial noun categories) yielded six significant clusters (see Table
\ref{tab:res-ao-group1}, Figure \ref{fig:group-slices}).
% overlap with ROI
Two homologous clusters are located in the anterior part of the PPA group
overlap.
% in detail
Specifically, these clusters are located at the borders of the posterior
parahippocampal cortex, the occipital and temporal fusiform gyrus and lingual
gyrus.\todo{Havard-Oxford atlas: 3 different most prob. locations depen. on
voxel}
% precuneus
Two additional homologous clusters are apparent in the ventral precuneus
extending into the retrosplenial cortex.
% LOC
Finally, two homologous clusters are located in the superior lateral occipital
cortex.

% figure group results primary AD & AV contrasts
\begin{figure*}[h!] \centering
    \includegraphics[width=\linewidth]{figures/group-slices}
    \caption{Mixed-effects group-level (N=14) GLM results. Significant clusters
        (Z>3.4, p<.05 cluster-corrected) are overlaid on the MNI152 T1-weighted
        head template (gray).
        Light gray: The audio-description's field of view
        (cf. \citep{hanke2014audiomovie}).
        Black: outline of overlapping individual PPA ROIs
        \citep{sengupta2016extension}.
        The results of audio-description's primary $t$-contrast (blue) that
        compares geometry-related nouns spoken by the narrator to non-spatial
        nouns (\texttt{geo, groom} > all non-spatial
        categories)
        are overlaid over the movie's primary $t$-contrast (blue) that compares
        cuts to a setting depicted for the first time with cuts within a
        recurring setting
        (\texttt{vse\_new > vpe\_old}).
        }
    \label{fig:group-slices}
\end{figure*}

\begin{table*}[h!]
\caption{Significant clusters (z-threshold Z>3.4; p<.05 cluster-corrected)
    of the primary $t$-contrast for the audio-visual movie comparing cuts to a
    setting depicted for the first time with cuts within a recurring setting
    (\texttt{vse\_new > vpe\_old}).
    Clusters sorted by voxel size.
    The first brain structure given contains the voxel with the maximum Z-Value,
    followed by brain structures from posterior to anterior, and partially
    covered areas (l. = left; r. = right; c. = cortex; g. = gyrus).}
\label{tab:res-av-group1}
\begin{tabular}{rrrrrrrrrp{3cm}}
\toprule
& & & \multicolumn{3}{r}{max location (MNI)} & \multicolumn{3}{r}{center of gravity (MNI)} &
\\ \cmidrule{4-6} \cmidrule{7-9}
voxels & $p_{corr.}$ & Z-max & x & y & z  & x & y & z & structure \\
\midrule
3003 & 0 & 5.31 & 22.5 & -45.5 & -12 & 4.53 & -63.3 & -3.72 & r. lingual g.; r.
cuneal c., intracalcarine c., bilaterally occipital fusiform g., precuneus,temporal fusiform c., posterior parahippocampal c.  \\
154 & 0.000000656 & 4.46 & -35 & -83 & 28 & -32.8 & -86.2 & 21.4 & l. superior lateral occipital c. \\
121 & 0.00000769 & 4.65 & 25 & -80.5 & 25.5 & 23.7 & -83.8 & 25.4 & r. superior lateral occipital cortex \\
\bottomrule
\end{tabular}
\end{table*}

@@

% intro
Third, we investigated result from both naturalistic paradigms on the level of
individual subjects to ensure that the group results are not just a by-product
of the averaging process.
% AD is the real shit
Further, we hypothesized that an exclusively auditory stimulus could localize
the PPA in individual subjects and thus possibly substitute a classic visual
localizer experiment.
% Sengupta et al., 2016; unilateral in sub-04 and sub-20
The visual localizer yielded bilateral parahippocampal clusters in 12 of 14
subjects and an unilateral right clusters in two subjects (cf. Table 3 in
\citep{sengupta2016extension}).
% Sengupta: 1 of 3
Individual PPAs were assessed by visually inspecting thresholded $t$-maps
(Z>1.64, p<.05 cluster corrected) of three different $t$-contrasts, and
titrating\todo{??} the $t$-threshold in the range of [2, 3] in until we found an
isolated cluster (cf. Table 3 in that matched the expected anatomical location
based on literature \citep{epstein1998ppa}.

% one contrast to localize them all; "...and Z>3.4 for all"
Contrary to \citep{sengupta2016extension}, we here used the same contrast of
each naturalistic stimulus and the same threshold for all subjects.
% subject space -> NeuroVault
Results of the analyses that were performed in subject-space can be found in the
accompanying dataset (Z>2.3, p<.05 cluster-corrected).
% here report in group space
For better comparisons of subjects, we here report results from the analyses
performed in group space (Z>3.4, p<.05 cluster-corrected).
% ref to figure
Figure \ref{fig:subs-thresh-ppa} depicts thresholded $z$-maps of the primary AV
and AD $t$-contrast, and the outline of overlapped, individual PPAs
co-registered to the MNI152 template.
% one slice to show them all
Transversal slice of z=-11 was chosen as it depicts [at least some] voxels of
significant clusters in almost all subjects.

@@

\begin{figure*}[h!]
\centering
    \includegraphics[width=\linewidth]{figures/subs-thresh-ppa}
    \caption{Fixed-effects individual-level GLM results (Z>3.4, p<.05
        cluster-corrected).
        Individual brains are aligned via non-linear
        transformation to a study-specific T2* group template that is
        co-registered to the MNI152 template with an affine transformation (12
        degrees of freedom).
        The results of the audio-description's primary
        $t$-contrast (blue) that compares geometry related nouns to non-
        geometry related nouns spoken by the narrator
        (\texttt{geo, groom > all non-geo}) are overlaid over the movie's
        primary $t$-contrast (blue) that compares cuts to setting depicted for
        the first time with cuts within a recurring setting
        (\texttt{vse\_new > vpe\_old}).
        Black:
        outline of subject-specific PPA ROIs.
        Light gray: The
        audio-description's field of view (cf. \citep{hanke2014audiomovie}).
        To facilitate comparisons across subjects, we chose the same horizontal
        slice (x=-11) for all subjects as this slice depicts voxels of
        significant clusters in almost all subjects.
        The figure does not show voxels of the left cluster of the AV stimulus
        in sub-09 and sub-18, and voxels of the right cluster of the AV
        stimulus in sub-15.}
    \label{fig:subs-thresh-ppa}
\end{figure*}

% Bland-Altman-Plots
To better depict the agreement and difference between the results of the visual
localizer and the primary AD contrast, we created a Bland-Altman-Plot for every
subject (see Figure \ref{fig:bland-altman}).
% what it depicts
Each subplot visualizes the mean value and difference (localizer minus AD) of
two spatially corresponding voxels in the unthresholded $z$-maps.
% top KDE plot
A shift of the distribution to voxels with a mean above zero can be seen the
further we constrain voxels to the individual PPA (cf. KDE plot for the x-axes).
% right KDE plot
Values above the horizontal line depict voxels that show a higher $z$-value in
the dedicated localizer, values below the horizontal line depict voxels that
show a higher $z$-value in the AD stimulus.

\begin{figure*}[h!]
\centering
    \includegraphics[scale=0.27]{figures/subjs_bland-altman.png}
    \caption{Bland-Altman-Plots for individual subjects.
    The x-axes show the means of two spatially corresponding voxels in the
    unthresholded $z$-map of the audio-description's primary contrast and
    unthresholded $z$-map of the visual localizer (KDE plot on the top).
    The y-axes show the difference of two voxels (localizer minus
    audio-description; KDE plot on the right).
    The overlays depict voxels spatially constrained to the
    temporal and occipital cortex (gray; based on probabilistic Jülich
    Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment}),
    PPA overlap of all subjects (blue),
    and individual PPA(s) (red).}
    \label{fig:bland-altman}
\end{figure*}
